Efficient evaluation of threshold queries of derived fields in a numerical simulation database

### 2014-09-04 paper.tex
Moved JHTDB section. Work on Science use case section.

Similar to the vorticity there are other fields of interest, which can be thresholded. These include ...

@@

>>>>

@@

In addition to obtaining the regions of largest vorticity there is substantial interest in studying the regions with highest values for other fields, such as
the second and third velocity gradient invariants ($Q$ and $R$). These invariants are scalar quantities whose values contain information about the 
topology of the flow and the rates of vortex stretching and rotation. In MHD finding the locations with largest values for the electric current
can lead to new insights into the development of the most intense reconnection events of magnetic field sheets in the simulated plasma. Similarly to
the vorticity the electric current is derived from the magnetic field by taking its curl. The list of fields of interest, which scientists would like to perform 
threshold queries on certainly does not stop here and is indicative of how valuable this functionality is in the study of turbulence and fluid dynamics.
